A Comparison of Dimensionality Reduction Techniques for Robotic Motion Planning

### 2016-05-13 paper/paper.tex
got rid of prm*

We used PRM* and RRTConnect in our project.

\subsection{PRM*}

The Probabilistic RoadMap algorithm has two phases: the preprocessing phase in
which a roadmap is constructed by sampling random points in the C-space, and
the query phase in which a graph search over the roadmap is made to connect
initial and goal configurations \cite{kavraki1996prm}. The map is constructed
during the preprocessing phase by sampling random points in the C-space and
then adding them to the vertices in the roadmap within a certain radius of the
point. PRM can be elevated to the asymptotically optimal PRM*, which is
described in Alg~\ref{alg:PRMstar}, by defining the radius to be a function of
the number of vertices and the dimensionality of the space
\cite{karaman2011sampling}. Since PRM* is asymptotically optimal, its solution
will converge to the optimal path as time goes to infinity.

@@

\begin{algorithm}[ht] 
    \caption{$\Function{PRM}^*$~\cite{karaman2011sampling}}
    \label{alg:PRMstar}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

        \STATE $V \leftarrow \{x_{\Var{init}}\} \cup \{\Var{SampleFree}_i\}_{i=1,\ldots,n}$
        \STATE $E \leftarrow \emptyset$
        \FORALL{$v \in V$}
            \STATE $U \leftarrow \Function{Near}(G = (V, E), v,
            \gamma \cdot \Function{PRM}(\log(n) / n) ^ {1 / d})
            \backslash \{v\}$
            \FORALL{$u \in U$}
                \IF{$\Function{CollisionFree}(v, u)$}
                    \STATE $E \leftarrow E \cup \{(v, u), (u, v)\}$
                \ENDIF
            \ENDFOR
        \ENDFOR
        \RETURN $G = (V, E)$

>>>>

We used PRM and RRTConnect in our project.

\subsection{PRM}

The Probabilistic RoadMap algorithm has two phases: the preprocessing phase in
which a roadmap is constructed by sampling random points in the C-space, and
the query phase in which a graph search over the roadmap is made to connect
initial and goal configurations \cite{kavraki1996prm}. The map is constructed
during the preprocessing phase by sampling random points in the C-space and
then adding them to the vertices in the roadmap within a certain radius of the
point. The algorithm is described in Alg~\ref{alg:PRM}.
%PRM can be elevated to the asymptotically optimal PRM*, which is
%described in Alg~\ref{alg:PRMstar}, by defining the radius to be a function of
%the number of vertices and the dimensionality of the space
%\cite{karaman2011sampling}. Since PRM* is asymptotically optimal, its solution
%will converge to the optimal path as time goes to infinity.

@@

\begin{algorithm}[ht] 
    \caption{$\Function{PRM}~\cite{karaman2011sampling}}
    \label{alg:PRM}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

        \STATE $V \leftarrow \{x_{\Var{init}}\} \cup \{\Var{SampleFree}_i\}_{i=1,\ldots,n}$
        \STATE $E \leftarrow \emptyset$
        \FORALL{$v \in V$}
            \STATE $U \leftarrow \Function{Near}(G = (V, E), x_{rand}, r);$
            \STATE $ V \leftarrow V \cup {x_{rand}} $
            \FORALL{$u \in U $}
                \IF{$\Function{CollisionFree}(v, u)$}
                    \STATE $E \leftarrow E \cup \{(v, u), (u, v)\}$
                \ENDIF
            \ENDFOR
        \ENDFOR
        \RETURN $G = (V, E)$
